Deep Learning

### 2015-01-06 2014/nature-review/deepreview.tex
word embedding figure + start working on refs

\documentclass[]{article}
\usepackage{epsfig}
\usepackage{graphicx}
\parskip 0.1in
\parindent 0.0in
\setcounter{secnumdepth}{1}
\title{Deep Learning}

@@

Deep learning is currently making major advances in solving problems that
have resisted the best attempts of the Artificial Intelligence community
for many years. Deep learning is very good at discovering intricate
structure in large, high-dimensional datasets and is therefore widely
applicable in all of the sciences. For example, it beats all previous
machine learning techniques at predicting the activity of potential drug
molecules~\cite{Dahl}, detecting new fundamental particles~\cite{??},
classifying galaxies~\cite{??}, or predicting the effects of mutations in
non-coding DNA on gene expression and disease~\cite{Frey}.

@@

Interest in recurrent networks (which are deep in time) was revived by
``Long Short Term Memory'' networks (LSTMs) that use special hidden units
whose natural behaviour is to remember inputs for a long
time~\cite{Hochreiter+Schmidhuber-1997}.  
A linear ``memory cell'' interacts with other units
via gated connections whose weights are multiplied by the state of a
logistic gating unit that has an activation between $0$ and $1$. The input
vector has little effect on the state of a memory cell if the cell's input
gate has a low activation so memory cells can learn to selectively ignore
the input.  Similarly, a memory cell has little effect on the output if its
output gate has low activation. Each memory cell also has a connection to
itself at the next time-step that has a weight of 1 so it tends to copy its
own real-valued state, but this connection is gated by a ``keep gate'' so
the stored value is quickly eroded unless the keep-gate has an activation
near $1$.  The gates themselves have their activities determined by
weighted inputs that they receive from the input vectors and all of the
memory cells.

@@

% YB: I would skip the next paragraph; we've tried this and failed
% so maybe it is better to wait and see before we put this in a review
It is not yet clear which aspects of the complicated architecture of LSTMs
are really necessary. Memory cells are a good way of allowing the
backpropagated error derivatives to neither explode nor vanish, but they
are not the only way.  For example, recurrent nets with rectified linear
hidden units that use the non-linear function $y=max(0,x)$ are much simpler
than LSTMs and if the recurrent weight matrix is initialized to be close to
the identity matrix they work about as well as LSTMs both for toy problems
involving very long-range temporal structure and for real tasks like
predicting the next word in text\cite{LeHinton}.

@@

%%%%%%%% YOSHUA %%%%%%%
YOSHUA: Add about 300 words plus t-sne figure of words and/or phrases.

@@

After your stuff on language, I would like to include some version of the
paragraph below along with a figure.
%%%%%%%%%%%%%%%%%%%%%%%

@@

Human vision is an active process in which intelligent fixations are used
to ensure that only a tiny fraction of the optic array is ever processed at
high resolution. We expect much of the future progress in vision,
especially for video understanding or robotics, to come from systems that
are trained end-to-end and combine deep convolutional networks with
recurrent nets that use reinforcement learning to decide where to
look\cite{}.  Such systems already outperform passive vision
systems\cite{ba\&mnih}.  Similarly, when understanding sentences or whole
documents we expect future systems to learn strategies for selectively
attending to one part at a time~\cite{Bahdanau-et-al-arxiv2014}. We also expect
that in the next few years deep recurrent neural networks will become far
better at understanding the meaning of documents, including the way in
which the thoughts expressed by the sentences are related to one another.

This review has focused on supervised learning because of its recent
achievements and we have ignored much interesting work on unsupervised
learning procedures for deep neural networks~\cite{deep-boltz, wake-sleep,
  google-cat, denoising-auto, ranzato-pami, more recent}. In the long run,
however, we believe unsupervised learning will be essential for allowing
deep networks to generalize well by creating internal representations that
untangle the many different factors that interact to produce images, speech
and documents~\cite{Yann, Yoshua: untangling papers,Bengio-Courville-Vincent-TPAMI2013}.

@@

>>>>

\documentclass[]{article}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{natbib}

\parskip 0.1in
\parindent 0.0in
\setcounter{secnumdepth}{1}
\title{Deep Learning}

@@

Deep learning is currently making major advances in solving problems that
have resisted the best attempts of the Artificial Intelligence community
for many years. Deep learning is very good at discovering intricate
structure in large, high-dimensional datasets and is therefore widely
applicable in all of the sciences. For example, it has beaten previous
machine learning techniques at predicting the activity of potential drug
molecules~\cite{Dahl}, detecting new fundamental particles~\cite{??},
classifying galaxies~\cite{??}, or predicting the effects of mutations in
non-coding DNA on gene expression and disease~\cite{Frey}.

@@

Interest in recurrent networks (which are deep in time) was revived by
``Long Short Term Memory'' networks (LSTMs) that use special hidden units
whose natural behaviour is to remember inputs for a long
time~\cite{Hochreiter+Schmidhuber-1997}.  
A linear ``memory cell'' interacts with other units
via gated connections whose weights are multiplied by the state of a
logistic gating unit that has an activation between $0$ and $1$. The input
vector has little effect on the state of a memory cell if the cell's input
gate has a low activation so memory cells can learn to selectively ignore
the input.  Similarly, a memory cell has little effect on the output if its
output gate has low activation. Each memory cell also has a connection to
itself (it is a leaky neuron) at the next time-step that has a weight of 1 so it tends to copy its
own real-valued state, but this self-connection is gated by a ``keep gate'' so
the stored value leaks quickly unless the keep-gate has an activation
near $1$.  The gates themselves have their activities determined by
weighted inputs that they receive from the input vectors and all of the
memory cells.

@@

Recent work~\citep{Chung-et-al-NIPSDL2014} suggests that not all the elements of the LSTM
architecture are required, the crucial element being the presence of
of the gate controlling the leaking rate (or time constant) of the cell.
%It is not yet clear which aspects of the complicated architecture of LSTMs
%are really necessary. Memory cells are a good way of allowing the
%backpropagated error derivatives to neither explode nor vanish, but they
%are not the only way.  For example, recurrent nets with rectified linear
%hidden units that use the non-linear function $y=max(0,x)$ are much simpler
%than LSTMs and if the recurrent weight matrix is initialized to be close to
%the identity matrix they work about as well as LSTMs both for toy problems
%involving very long-range temporal structure and for real tasks like
%predicting the next word in text\cite{LeHinton}.

@@

\iffalse
%%%%%%%% YOSHUA %%%%%%%
YOSHUA: Add about 300 words plus t-sne figure of words and/or phrases.

@@

After your stuff on language, I would like to include some version of the
paragraph below along with a figure.
%%%%%%%%%%%%%%%%%%%%%%%
\fi

\begin{figure}[H]
\centerline{\includegraphics[width=0.7\linewidth]{word-embeddings.png}}
\caption{Illustration of word representations learned for modeling
language, non-linearly projected to 2-D for visualization.}
\end{figure}

@@

Human vision is an active process in which intelligent fixations are used
to ensure that only a tiny fraction of the optic array is ever processed at
high resolution. We expect much of the future progress in vision,
especially for video understanding or robotics, to come from systems that
are trained end-to-end and combine deep convolutional networks with
recurrent nets that use reinforcement learning to decide where to
look\cite{}.  Such systems already outperform passive vision
systems\cite{ba+mnih}.  Similarly, when understanding sentences or whole
documents we expect future systems to learn strategies for selectively
attending to one part at a time~\cite{Bahdanau-et-al-arxiv2014}. We also expect
that in the next few years deep recurrent neural networks will become far
better at understanding the meaning of documents, including the way in
which the thoughts expressed by the sentences are related to one another.

This review has focused on supervised learning because of its recent
achievements and we have ignored much interesting work on unsupervised
learning procedures for deep neural networks~\cite{deep-boltz, wake-sleep,
  google-cat, denoising-auto, ranzato-pami, more recent}. In the long run,
however, we believe unsupervised learning will be essential for allowing
deep networks to generalize well by creating internal representations that
untangle the many different factors that interact to produce images, speech
and documents~\cite{Yann,Bengio-Courville-Vincent-TPAMI2013}.

@@

\bibliography{strings,ml,aigaion}
\bibliographystyle{natbib}
